Generating Random Logic Programs Using Constraint Programming

### 2020-05-11 text/paper2/paper.tex
Move config variables to the Config class
Refactoring
Integrate program generation and fact generation
Gathering experimental data
Some new plots

% TODO (for later)
% 1) Use American English
% 2) Avoid the Definition environment (to save space)

% Empirical tasks:
% 1) make the CP model faster: apply the redundant constraints to predicates
% (not just variables). Check if everything works out.
% 2) motivate either for benchmarking or by comparing parameter learning with
% ProbFOIL
% New things I could talk about:
% 1) entailment for conditional independence
% 2) the 'required formula' part of the model

@@

\begin{figure}[t]
  \centering
  \input{impact.tex}
  \caption{The mean number of nodes in the binary search tree for each value of
    each experimental parameter. Note that the horizontal axis is on a $\log_2$
    scale.}
  \label{fig:impact}
\end{figure}

>>>>

% TODO: does the restart policy still matter? If so, update the numbers.
% TODO (for later)
% 1) Use American English
% 2) Avoid the Definition environment (to save space)

% Description of experimental options
% Old options: (<600k experiments)
% number of predicates (2, 4, 8)
% number of variables (2, 4, 8)
% max number of nodes (2, 4, 8)
% max arity (1, 2, 3)
% number of constants (0)
% number of additional clauses (0)
% number of independent pairs (all options)
% New options:
% define each predicate: true
% allow empty bodies: false
% timeout = 60s (for both?)
% disable negative cycles
% probabilities = [0.1, ..., 0.9]
% generate 10 programs (with restarts, restarting arities and independent pairs)
% domain size: 100, 200, 400
% proportion probabilistic: 0.25, 0.5, 0.75
% number of facts: 1k, 10k, 100k
% DERIVATIVE: average spots per constant
% DERIVATIVES: universe size, proportion listed
% NOTE: The distribution of facts is uniformly distributed across predicates
% (because it's easier this way)
% NOTE: number of facts goes up to 75% of the universe

% Empirical tasks:
% 1) make the CP model faster: apply the redundant constraints to predicates
% (not just variables). Check if everything works out.
% 2) motivate either for benchmarking or by comparing parameter learning with ProbFOIL
% 3) create a constraint for groundedness (see the ProbLog FAQ)
% New things I could talk about:
% 1) entailment for conditional independence
% 2) the 'required formula' part of the model

@@

\begin{figure}[t]
  \centering
  \begin{minipage}[t]{.49\textwidth}
    \centering
    \input{impact.tex}
    \captionof{figure}{The mean number of nodes in the binary search tree for
      each value of each experimental parameter. Note that the horizontal axis
      is on a $\log_2$ scale.}
    \label{fig:impact}
  \end{minipage}
  \hfill
  \begin{minipage}[t]{.49\textwidth}
    \centering
    \input{bars.tex}
    \captionof{figure}{Inference time for different values of $\maxArity{}$ and
      proportions of facts that are probabilistic. The total number of facts is
      fixed at $10^5$.}
    \label{fig:bars}
  \end{minipage}
\end{figure}

\begin{figure}[t]
  \centering
  \input{line_plots.tex}
  \caption{Mean inference time for a range of ProbLog inference algorithms as
    a function of the total number of facts in the program and the proportion of
    independent pairs of predicates. For the second plot, the number of facts is
    fixed at $10^5$.}
  \label{fig:line_plots}
\end{figure} % TODO: describe in the text
